\mytitle{}

### 2019-07-29 paper/infocom.tex
Algo compare, even more trimming.

\begin{figure}
	\centering
	\resizebox{0.9\linewidth}{!}{\begin{tikzpicture}
		\node(remote){Remote};

@@

	\resizebox{0.5\linewidth}{!}{
		\begin{tabular}{@{}ll@{}}
			\toprule
			New Feature (unit) & Range \\
			\midrule
			Load (\si{\mega\bit\per\second}) & $[0, U_s]$ \\
			IP & $[0, 2^{32}-1]$ \\
			Last Action (\si{\percent}) & $[0, 1]$ \\
			Duration (\si{\milli\second}) & $[0, \num{2000}]$ \\
			Size (\si{\mebi\byte}) & $[0,10]$ \\
			Correspondence Ratio & $[0,1]$ \\
			Mean IAT (\si{\milli\second}) & $[0, \num{10000}]$ \\
			$\Delta$In/Out Rate (\si{\mega\bit\per\second}) & $[-50, 50]$ \\
			Packets In/Out & $[0, 7000]$ \\
			Packets In/Out Window & $[0, 2000]$ \\
			Mean In/Out Packet Size (\si{\byte}) & $[0, 1560]$ \\
			\bottomrule
		\end{tabular}
	}
	\vspace{-1em}
\end{table}

@@

We compare our work's performance and learning rate against Marl \cite{DBLP:journals/eaai/MalialisK15}, the state-of-the-art in RL-based DDoS prevention, across different topologies and workloads.
We made use of the OPUS and TCP traffic models introduced in \cref{sec:a-new-normal}, both topologies discussed below (1-dest vs Fat-Tree), and varied the amount of hosts communicating over each ingress/egress node---different networks will impose different levels of host density, e.g., popular web servers may have many more clients than egress points from their network.
Additionally, we evaluated our new models in multi-agent (\emph{separate}, no model sharing) and i single-agent modes (\emph{single}, 0-cost perfect information sharing).
In each case, the algorithm's performance was averaged over \num{10} episodes of length \num{10000} timesteps (resetting policies between episodes).
Host allocations at the beginning of each episode were generated pseudorandomly to ensure fairness between episodes.
Malicious traffic is generated by \emph{hping3} program, generating UDP-flood traffic targeting random ports with MTU-sized packets, mapping to the large frame sizes expected in an amplification attack.

All experiments were executed on Ubuntu 18.04.2 LTS (GNU/Linux 4.4.3-040403-generic x86\_64), using a 4-core Intel Core i7-6700K (clocked at \SI{4.2}{\giga\hertz}) and \SI{32}{\gibi\byte} of RAM.
%All code underpinning these findings is available on a public repository\footnote{\url{https://github.com/FelixMcFelix/rln-dc-ddos-paper}}.
%All code underpinning these findings is available on a public repository.\footnote{Private until publication.}

@@

\subsection{Parameters}
Algorithm parameters were set at $\alpha=0.05$, linearly annealing $\epsilon=0.2 \rightarrow 0$ by $t=3000$ in the case of Marl (\num{8000} actions per agent in the \emph{Instant/Guarded} models).
Benign hosts uploaded between \SIrange{0}{1}{\mega\bit\per\second}, and hosts were redrawn each episode with $\operatorname{P}(\mathit{malicious})=0.4$.
Malicious hosts sent \SIrange{2.5}{6}{\mega\bit\per\second} when attacking UDP traffic, increased to \SIrange{4}{7}{\mega\bit\per\second} when using TCP-like or mixed traffic to meaningfully impact benign flows.
Given $n$ and $\operatorname{P}(\mathit{malicious})$, we see an expected malicious bandwidth \numrange{1.27}{1.87} and \SIrange{2.03}{2.18}{$\! \times U_s$} respectively.
$U_s$ was fixed at $N_{\mathit{hosts}}+2$ \si{\mega\bit\per\second} (to account for burstiness), and each link had a delay of \SI{10}{\milli\second}.
All links had unbounded capacity, save for server-switch connections.
These parameter choices match those of the original study for direct comparison, but we justify our range of $n$ as capturing increasing scales of host activity.

@@

\subsection{Congestion-unaware traffic}
%\begin{figure}
%	\centering
%	\includegraphics[width=0.9\linewidth]{../plots/udp-2}
%	
%	\caption{
%		Online performance for $n=2$ hosts per egress point when benign traffic is UDP-like.
%		Although Marl++ offers a marked improvement (a peak $\sim$\SI{30}{\percent} more benign traffic arrives unimpeded), SPF significantly underperforms for this relatively simple topology.
%		Non-SPF agents start off reasonably well, slowly learning better policies.
%		\label{fig:udp-2}
%	}
%\end{figure}
%\begin{figure}
%	\centering
%	\includegraphics[width=0.9\linewidth]{../plots/udp-16}
%	
%	\caption{
%		Online performance for $n=16$ hosts per egress point when benign traffic is UDP-like.
%		Marl++ remains marginally ahead of its predecessor, though both have undergone a significant drop in effectiveness.
%		SPF, remarkably, displays performance on par with Marl++ for this more difficult topology.
%		Both of the new models take longer to train, but achieve better peak and average performance than Marl.
%		\label{fig:udp-16}
%	}
%\end{figure}
\begin{figure}
	\centering
	\includegraphics[width=0.8\linewidth]{../plots/tnsm-udp-box-separate}
	\vspace{-1em}
	\caption{
		Online performance for Opus benign traffic in a single-destination network, multi-agent mode.
%		Marl++ offers a marked improvement (a peak $\sim$\SI{30}{\percent} more benign traffic arrives unimpeded) at small $n$, and remains marginally ahead of its predecessor by $n=16$, though both have undergone a significant drop in effectiveness.
		\emph{Instant} outperforms Marl for $n \in \{4, 8\}$ (with higher variance), but performs similarly to Marl at $n\in \{2, 16\}$.
		Here, \emph{Guarded} always underperforms compared to the other agent designs.
%		SPF, remarkably, slightly outperforms Marl++ (with lower variance) for this more difficult topology despite being worse for smaller $n$.
%		Both of the new models take longer to train, but achieve better peak and average performance than Marl.
%		?? REWORK/MAKE ACCURATE
		\vspace{-1em}
		\label{fig:udp-tree-box}
	}
\end{figure}

@@

\subsection{Congestion-aware traffic}
%\begin{figure}
%	\centering
%	\includegraphics[width=0.9\linewidth]{../plots/tcp-2}
%	
%	\caption{
%		Online performance for $n=2$ hosts per egress point when benign traffic is TCP-like.
%		Marl++ and Marl achieve very similar performance, starting off similarly well without notable improvement over an episode.
%		SPF's performance is disappointingly close to baseline, indicating that it is as useful as having no defence system.
%		\label{fig:tcp-2}
%	}
%\end{figure}
\begin{figure}
	\centering
	\includegraphics[width=0.8\linewidth]{../plots/tnsm-tcp-box-single}
	\vspace{-1em}
	\caption{
		Online performance for HTTP benign traffic in a single-destination network, single-agent mode.
%		\emph{Instant} and \emph{Guarded} exhibit essentially identical efficacy at $n~=~2$, protecting less traffic than Marl.
		Only \emph{Guarded}'s performance rapidly increases with $n$, achieving considerably better median performance and lower variance than the other models.
		Longer tails of outliers typically indicate longer training times---we observe that \emph{Guarded} has considerably lower variance once it has converged on a stable policy.
		\vspace{-1em}
		\label{fig:tcp-tree-box}
	}
\end{figure}
%\begin{figure}
%	\centering
%	\includegraphics[width=0.95\linewidth]{../plots/tnsm-tcp-box-single}
%	
%	\caption{
%		Online performance for HTTP benign traffic in a single-destination network, single-agent mode.
%		?? DO I need this?
%		\label{fig-tcp-tree-box-single}
%	}
%\end{figure}
\begin{figure}
	\centering
	\includegraphics[width=0.8\linewidth]{../plots/tnsm-tcp-16-single}
	\vspace{-1em}
	\caption{
		Online performance of standard and single-agent models over time in a single-destination network with $n=16$ hosts per egress point and HTTP benign traffic.
%		At this level of host density, \emph{Guarded} reaches higher peak performance sooner and is considerably more consistent throughout the episode.
%		\emph{Guarded} benefits greatly from information sharing, converging to protect around \SI{75}{\percent} of TCP traffic within \SI{100}{\second}.
%		The \emph{Instant} model converges to Marl's level of performance.
%		With a single agent, Marl++ shows worse performance, while SPF improves significantly and continues to learn well past annealing $\epsilon \rightarrow 0$.
		\vspace{-1em}
		\label{fig:tcp-tree-16}
	}
\end{figure}

@@

\subsection{RL algorithms}
When choosing a learning algorithm, we compared semi-gradient Sarsa against Q-learning.
Preliminary experiments found that Sarsa offered the best performance and behaviour.
?? Link plot or table w Sarsa vs. Q results.

@@

\emph{Athena} \cite{DBLP:conf/dsn/LeeKSPY17} is a general SDN framework for intrusion detection, using a \emph{k-nearest neighbours} classifier to detect individual attack flows.
Although heavyweight (and effective compared with \textcite{DBLP:conf/lcn/BragaMP10}), their comparison against SPIFFY lacks the evidence needed to understand how the systems compare.

>>>>

\begin{figure}
	\centering
	\resizebox{0.8\linewidth}{!}{\begin{tikzpicture}
		\node(remote){Remote};

@@

	\resizebox{0.45\linewidth}{!}{
		\begin{tabular}{@{}ll@{}}
			\toprule
			New Feature (unit) & Range \\
			\midrule
			Load (\si{\mega\bit\per\second}) & $[0, U_s]$ \\
			IP & $[0, 2^{32}-1]$ \\
			Last Action (\si{\percent}) & $[0, 1]$ \\
			Duration (\si{\milli\second}) & $[0, \num{2000}]$ \\
			Size (\si{\mebi\byte}) & $[0,10]$ \\
			Correspondence Ratio & $[0,1]$ \\
			Mean IAT (\si{\milli\second}) & $[0, \num{10000}]$ \\
			$\Delta$In/Out Rate (\si{\mega\bit\per\second}) & $[-50, 50]$ \\
			Packets In/Out & $[0, 7000]$ \\
			Packets In/Out Window & $[0, 2000]$ \\
			Mean In/Out Packet Size (\si{\byte}) & $[0, 1560]$ \\
			\bottomrule
		\end{tabular}
	}
	\vspace{-1em}
\end{table}

@@

We compare our work's performance and learning rate against Marl \cite{DBLP:journals/eaai/MalialisK15}, the state-of-the-art in RL-based DDoS prevention, across different topologies and workloads.
We made use of the OPUS and TCP traffic models introduced in \cref{sec:a-new-normal}, both topologies discussed below (1-dest vs Fat-Tree), and varied the amount of hosts communicating over each egress node.
Additionally, we evaluated these models in multi-agent (\emph{separate}, no model sharing) and single-agent modes (\emph{single}, 0-cost perfect information sharing).
In each case, the algorithm's performance was averaged over \num{10} episodes of length \num{10000} timesteps (resetting policies between episodes).
Host allocations at the beginning of each episode were generated pseudorandomly to ensure fairness between episodes.
Malicious traffic is provided by \emph{hping3}, generating UDP-flood traffic targeting random ports with MTU-sized packets.
All experiments were executed on Ubuntu 18.04.2 LTS (GNU/Linux 4.4.3-040403-generic x86\_64), using a 4-core Intel Core i7-6700K (clocked at \SI{4.2}{\giga\hertz}) and \SI{32}{\gibi\byte} of RAM.
%All code underpinning these findings is available on a public repository\footnote{\url{https://github.com/FelixMcFelix/rln-dc-ddos-paper}}.
%All code underpinning these findings is available on a public repository.\footnote{Private until publication.}

@@

\subsection{Parameters}
Algorithm parameters were set at $\alpha=0.05$, linearly annealing $\epsilon=0.2 \rightarrow 0$ by $t=3000$ in the case of Marl (\num{8000} actions per agent in the \emph{Instant/Guarded} models).
Benign hosts uploaded between \SIrange{0}{1}{\mega\bit\per\second}, and hosts were redrawn each episode with $\operatorname{P}(\mathit{malicious})=0.4$.
Malicious hosts sent \SIrange{2.5}{6}{\mega\bit\per\second} when attacking UDP traffic, increased to \SIrange{4}{7}{\mega\bit\per\second} for TCP-like or mixed traffic to meaningfully impact benign flows.
Given $n$ and $\operatorname{P}(\mathit{malicious})$, we see an expected malicious bandwidth \numrange{1.27}{1.87} and \SIrange{2.03}{2.18}{$\! \times U_s$} respectively.
$U_s$ was fixed at $N_{\mathit{hosts}}+2$ \si{\mega\bit\per\second} (to account for burstiness), and each link had a delay of \SI{10}{\milli\second}.
All links had unbounded capacity, save for server-switch connections.
These parameter choices match those of the original study for direct comparison, but we justify our range of $n$ as capturing increasing scales of host activity.

@@

\subsection{Congestion-unaware traffic}
%\begin{figure}
%	\centering
%	\includegraphics[width=0.9\linewidth]{../plots/udp-2}
%	
%	\caption{
%		Online performance for $n=2$ hosts per egress point when benign traffic is UDP-like.
%		Although Marl++ offers a marked improvement (a peak $\sim$\SI{30}{\percent} more benign traffic arrives unimpeded), SPF significantly underperforms for this relatively simple topology.
%		Non-SPF agents start off reasonably well, slowly learning better policies.
%		\label{fig:udp-2}
%	}
%\end{figure}
%\begin{figure}
%	\centering
%	\includegraphics[width=0.9\linewidth]{../plots/udp-16}
%	
%	\caption{
%		Online performance for $n=16$ hosts per egress point when benign traffic is UDP-like.
%		Marl++ remains marginally ahead of its predecessor, though both have undergone a significant drop in effectiveness.
%		SPF, remarkably, displays performance on par with Marl++ for this more difficult topology.
%		Both of the new models take longer to train, but achieve better peak and average performance than Marl.
%		\label{fig:udp-16}
%	}
%\end{figure}
\begin{figure}
	\centering
	\includegraphics[width=0.75\linewidth]{../plots/tnsm-udp-box-separate}
	\vspace{-1em}
	\caption{
		Online performance for Opus benign traffic in a single-destination network, multi-agent mode.
%		Marl++ offers a marked improvement (a peak $\sim$\SI{30}{\percent} more benign traffic arrives unimpeded) at small $n$, and remains marginally ahead of its predecessor by $n=16$, though both have undergone a significant drop in effectiveness.
%		\emph{Instant} outperforms Marl for $n \in \{4, 8\}$ (with higher variance), but performs similarly to Marl at $n\in \{2, 16\}$.
		\emph{Guarded} always underperforms.
%		SPF, remarkably, slightly outperforms Marl++ (with lower variance) for this more difficult topology despite being worse for smaller $n$.
%		Both of the new models take longer to train, but achieve better peak and average performance than Marl.
%		?? REWORK/MAKE ACCURATE
		\vspace{-1em}
		\label{fig:udp-tree-box}
	}
\end{figure}

@@

\subsection{Congestion-aware traffic}
%\begin{figure}
%	\centering
%	\includegraphics[width=0.9\linewidth]{../plots/tcp-2}
%	
%	\caption{
%		Online performance for $n=2$ hosts per egress point when benign traffic is TCP-like.
%		Marl++ and Marl achieve very similar performance, starting off similarly well without notable improvement over an episode.
%		SPF's performance is disappointingly close to baseline, indicating that it is as useful as having no defence system.
%		\label{fig:tcp-2}
%	}
%\end{figure}
\begin{figure}
	\centering
	\includegraphics[width=0.75\linewidth]{../plots/tnsm-tcp-box-single}
	\vspace{-1em}
	\caption{
		Online performance for HTTP benign traffic in a single-destination network, single-agent mode.
%		\emph{Instant} and \emph{Guarded} exhibit essentially identical efficacy at $n~=~2$, protecting less traffic than Marl.
%		Longer tails of outliers typically indicate longer training.
%		\emph{Guarded}'s performance rapidly increases with $n$, achieving considerably better median performance and lower variance than the other models.
%		Longer tails of outliers typically indicate longer training times---we observe that \emph{Guarded} has considerably lower variance once it has converged on a stable policy.
		\label{fig:tcp-tree-box}
	}
\vspace{-1em}
\end{figure}
%\begin{figure}
%	\centering
%	\includegraphics[width=0.95\linewidth]{../plots/tnsm-tcp-box-single}
%	
%	\caption{
%		Online performance for HTTP benign traffic in a single-destination network, single-agent mode.
%		?? DO I need this?
%		\label{fig-tcp-tree-box-single}
%	}
%\end{figure}
\begin{figure}
	\centering
	\includegraphics[width=0.75\linewidth]{../plots/tnsm-tcp-16-single}
	\vspace{-1em}
	\caption{
		Online performance of standard and single-agent models over time (TCP, $n=16$, tree).
%		At this level of host density, \emph{Guarded} reaches higher peak performance sooner and is considerably more consistent throughout the episode.
%		\emph{Guarded} benefits greatly from information sharing, converging to protect around \SI{75}{\percent} of TCP traffic within \SI{100}{\second}.
%		The \emph{Instant} model converges to Marl's level of performance.
%		With a single agent, Marl++ shows worse performance, while SPF improves significantly and continues to learn well past annealing $\epsilon \rightarrow 0$.
		\label{fig:tcp-tree-16}
	}
\vspace{-1em}
\end{figure}

@@

\subsection{RL algorithms}
When choosing a learning algorithm, we compared semi-gradient Sarsa against Q-learning, and variants of these algorithms based on \emph{eligibility traces} (Sarsa($\lambda$), Watkins's Q($\lambda$)).
Our experiments found that Sarsa offered the best performance and behaviour; \cref{fig:algo-spf-tcp} shows a trend observed across model choices and communication except for multiagent \emph{Instant} protection of TCP where Q-learning succeeds.

\begin{figure}
	\centering
	\includegraphics[width=0.75\linewidth]{../plots/tnsm-algo-spf-tcp}
	\vspace{-1em}
	\caption{
		Comparison of RL algorithms for \emph{Guarded} (TCP, $n=16$, tree).
		%		At this level of host density, \emph{Guarded} reaches higher peak performance sooner and is considerably more consistent throughout the episode.
		%		\emph{Guarded} benefits greatly from information sharing, converging to protect around \SI{75}{\percent} of TCP traffic within \SI{100}{\second}.
		%		The \emph{Instant} model converges to Marl's level of performance.
		%		With a single agent, Marl++ shows worse performance, while SPF improves significantly and continues to learn well past annealing $\epsilon \rightarrow 0$.
		\label{fig:algo-spf-tcp}
	}
\vspace{-1em}
\end{figure}

@@

\emph{Athena} \cite{DBLP:conf/dsn/LeeKSPY17} is a general SDN framework for intrusion detection, using a \emph{k-nearest neighbours} classifier to detect individual attack flows.
Although heavyweight (and effective compared with \textcite{DBLP:conf/lcn/BragaMP10}), their comparison against SPIFFY lacks the evidence needed to draw conclusions.
